---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sigvis

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/sigvis)](https://CRAN.R-project.org/package=sigvis)
<!-- badges: end -->

Create interactive visualisations that summarise mutational signature analyses

## Installation

You can install the development version of sigvis like so:

``` r
# install.packages('remotes')
remotes::install_github('selkamand/sigvis')
```

## Usage

### Visualise Signatures

```{r fig.height=4, fig.width=8}
library(sigverse)

# Load Signature 
signatures <- sig_load('COSMIC_v3.3.1_SBS_GRCh38')

# Visualise a single signature
sig_visualise(signatures[["SBS2"]], title = "SBS2")
```

### Visualise Decompositions

```{r fig.height=4, fig.width=8}
# Load library containing results of TCGA mutational signature analysis
library(TCGAdecomp)

# Load decompositions from sigstash
brca_decompositions <- decomp_load('BRCA')

# Visualise a decomposition
sig_visualise(
  brca_decompositions[['TCGA-D8-A1XU-01A-11D-A14K-09']], 
  class = "decomposition", 
  title = 'TCGA-D8-A1XU-01A-11D-A14K-09'
)
```

### Visualise a Signature Model

Visualise the decomposition expected from a signature model, where signature 'SBS2' explains 60% of the mutations in a sample, and 'SBS13' explains the remaining 40%

```{r fig.height=4, fig.width=8}

# Visualise a model (combination of signatures)

model = sig_combine(signatures, model = c('SBS2' = 0.6, 'SBS13' = 0.4))
sig_visualise(model, class = 'model')
```

