---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sigvis

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/sigvis)](https://CRAN.R-project.org/package=sigvis)
[![R-CMD-check](https://github.com/selkamand/sigvis/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/selkamand/sigvis/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Create interactive visualisations that summarise mutational signature analyses

## Installation

You can install the development version of sigvis like so:

``` r
if (!require("pak", quietly = TRUE))
    install.packages("pak")

pak::pak("selkamand/sigverse")
```

## Usage

### Visualise Signatures

```{r fig.height=4, fig.width=10}
library(sigvis)
library(sigstash)

# Load Signature
signatures <- sig_load("COSMIC_v3.3.1_SBS_GRCh38")

# Select just SBS2
SBS2 <- signatures[["SBS2"]]

# Plot
sig_visualise(signature = SBS2, title = "SBS2")
```



### Visualise catalogues

```{r fig.height=4, fig.width=10}
# Load library containing results of TCGA mutational signature analysis
library(TCGAcatalogues)


# Load a catalogue
tally <- catalogues_load("BRCA", type = "SBS_96")

# Select a single sample of interest
sample = "TCGA-5L-AAT1-01A-12D-A41F-09"
tally_single_sample <- tally[[sample]]

tally_single_sample

# Visualise Observed Mutational Profile
sig_visualise(tally_single_sample, class = "catalogue", title = sample)
```

### Visualise a Signature Model

Visualise the catalogue expected from a signature model, where signature 'SBS2' explains 60% of the mutations in a sample, and 'SBS13' explains the remaining 40%

```{r fig.height=4, fig.width=10}
# Load sigstats library for combining signature models
library(sigstats)

# Visualise a model (combination of signatures)
model = sig_combine(signatures, model = c('SBS2' = 0.6, 'SBS13' = 0.4))
sig_visualise(model, class = 'model', title = "Model", subtitle = "Combination of SBS2 (60%) and SBS13 (40%)")
```


### Visualise a Signature Model Against the Observed Mutation Catalogue

Visualise the catalogue expected from a signature model, where signature 'SBS2' explains 60% of the mutations in a sample, and 'SBS13' explains the remaining 40%, but overlay on top of the observed mutational process

```{r}
library(sigstats) # For combining signature models
library(sigstash) # For pulling signatures
library(TCGAcatalogues) # For pulling example TCGA catalogue data

# Load Signature
signatures <- sig_load("COSMIC_v3.3.1_SBS_GRCh38")

# Create a model (combination of signatures)
model <- sig_combine(signatures, model = c('SBS2' = 0.6, 'SBS13' = 0.4)) 
model_signature <- sig_combine_collapse_to_single_signature(model) # Should be an option in sig_combine

# Load a catalogue (Tally of variant types)
tally <- catalogues_load("BRCA", type = "SBS_96")

# Get tally of a single sample
sample = "TCGA-5L-AAT1-01A-12D-A41F-09"
tally_single_sample <- tally[[sample]]

# Visualise the overlay
sig_visualise_overlay(
  catalogue = tally_single_sample,
  signature = model_signature
)
```

