---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sigvis

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/sigvis)](https://CRAN.R-project.org/package=sigvis)
[![R-CMD-check](https://github.com/selkamand/sigvis/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/selkamand/sigvis/actions/workflows/R-CMD-check.yaml)
![GitHub Issues or Pull
Requests](https://img.shields.io/github/issues-closed/selkamand/ggoncoplot)
[![code size](https://img.shields.io/github/languages/code-size/selkamand/sigvis.svg)](https://github.com/selkamand/sigvis)
![GitHub last
commit](https://img.shields.io/github/last-commit/selkamand/sigvis)
<!-- badges: end -->

Create interactive visualisations that summarise mutational signature analyses

## Installation

You can install the development version of sigvis like so:

``` r
if (!require("pak", quietly = TRUE))
    install.packages("pak")

pak::pak("selkamand/sigverse")
```

## Usage

### Visualise Signatures

```{r fig.height=4, fig.width=10}
library(sigvis)
library(sigstash)

# Load Signature
signatures <- sig_load("COSMIC_v3.3.1_SBS_GRCh38")

# Select just SBS2
SBS2 <- signatures[["SBS2"]]

# Plot
sig_visualise(signature = SBS2, title = "SBS2")
```



### Visualise catalogues

```{r fig.height=4, fig.width=10}
# Load library containing results of TCGA mutational signature analysis
library(TCGAcatalogues)


# Load a catalogue
tally <- catalogues_load("BRCA", type = "SBS_96")

# Select a single sample of interest
sample = "TCGA-5L-AAT1-01A-12D-A41F-09"
tally_single_sample <- tally[[sample]]

tally_single_sample

# Visualise Observed Mutational Profile
sig_visualise(tally_single_sample, class = "catalogue", title = sample)
```

### Visualise a Signature Model

Visualise the catalogue expected from a signature model, where signature 'SBS2' explains 60% of the mutations in a sample, and 'SBS13' explains the remaining 40%

```{r fig.height=4, fig.width=10}
# Load sigstats library for combining signature models
library(sigverse)

# Visualise a model (combination of signatures)
model = sig_combine(signatures, model = c('SBS2' = 0.6, 'SBS13' = 0.4), format = "combined")
sig_visualise(model, class = 'model', title = "Model", subtitle = "Combination of SBS2 (60%) and SBS13 (40%)")
```


### Visualise a Signature Model Against the Observed Mutation Catalogue

Visualise the catalogue expected from a signature model, where signature 'SBS2' explains 60% of the mutations in a sample, and 'SBS13' explains the remaining 40%, but overlay on top of the observed mutational process

```{r fig.height=4, fig.width=10}
library(TCGAcatalogues) # For pulling example TCGA catalogue data

# Load Signature
signatures <- sig_load("COSMIC_v3.3.1_SBS_GRCh38")

# Create a model (combination of signatures)
model <- sig_combine(signatures, model = c('SBS2' = 0.6, 'SBS13' = 0.4), format = "signature")

# Load a catalogue (Tally of variant types)
tally <- catalogues_load("BRCA", type = "SBS_96")

# Get tally of a single sample
sample = "TCGA-5L-AAT1-01A-12D-A41F-09"
tally_single_sample <- tally[[sample]]

# Visualise the overlay
sig_visualise_compare_reconstructed_to_observed(
  catalogue = tally_single_sample,
  signature = model
)
```

### Visualise Bootstraps

```{r fig.height=4, fig.width=10}
# Small Example
bootstraps <- example_bootstraps()
sig_visualise_bootstraps(bootstraps)

# Larger (Horizontal) Example
colo829_bootstraps <- example_bootstraps_colo829()
sig_visualise_bootstraps(colo829_bootstraps, min_contribution_threshold = 0.05, pvalue = 0.05, horizontal = TRUE)
```


### Visualise Signature Dotplot

Visualise the contributions of a signature across an entire cohort (or a collection of bootstrap experiments)

```{r signature_dotplot, fig.height=4, fig.width=10}
dotplot_data <- example_dotplot_data()
sig_visualise_dotplot(
  dotplot_data, 
  col_sample = "sample", 
  col_contribution = "contribution",
  col_fill = "sample_info",
  palette_fill = c(sample_of_interest = "#D55E00", "cancer_type"="#009E73", "other" = "#000000"),
  sort_by = "palette_fill",
  xlab = "SBS2"
  )
```

### Visualise Signature + Bar

For explanatory signatures and similar samples. See [sigstory](https://github.com/selkamand/sigstory) for examples of why we need. 

```{r minified, fig.height=1.5, fig.width=3}
# Quick reference visualisation of SBS2 that explains 40% of a sample
sig_visualise_minified(signature = SBS2, proportion = 0.4)
```

