---
title: "Visualisation Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Visualisation Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sigvis)
library(sigstash)
library(TCGAdecomp)
```

**Warning:** this package is in early development and not ready for general use

## Background

Mutational signature analysis answers 6 key questions. Each answer can be summarized with a visualization.

1.  What is the **observed mutational profile** of a **single sample**
2.  Are there patterns in the **observed mutational profile** of a **cohort**?
3.  Which **samples** are my **sample of interest** most similar to with respect to their **observed mutational profile**?
4.  Does mutational signature analysis **produce a good quality model** from which we can draw robust inferences about a **single sample**?
5.  What does the **mutational signature model** of a sample say about a **single sample?**
6.  Are there patterns in the **mutational signature models** of a cohort?
7.  What does signature X look like?

## **Observed mutational profile**

1\. Single Sample Visualisation

```{r}

# Load a decomposition
tally <- decomp_load("BRCA", type = "SBS_96")

# Select a single dataframe of interest
sample = "TCGA-5L-AAT1-01A-12D-A41F-09"
tally_single_sample <- tally[[sample]]

tally_single_sample

# Visualise it
sig_visualise(tally_single_sample, class = "decomposition", title = sample)
```

2A. Cohort stacked bar

2B. Per channel feature distribution in cohort context (dotplots)

## Sample Similarity

3.  signature similarity tree / tsne

## Signature Model

### Quality

4A. Model vs Observed

4B. Residual Plot

4C. Bootstrap performance

### Inferences

5.  Signature Contribution Plot
6.  Signature composition stacked barplot (compatible with ggoncoplot)

## Signatures

### [**What does signature X look like?**]{.underline}

Often there'll be a mutational signature and want to visualise the profile.

For example lets plot the profile of signature SBS2 from COSMIC database (but same process will work for de-novo signatures)

```{r}
# Load Signature
signatures <- sig_load("COSMIC_v3.3.1_SBS_GRCh38")

# Select just SBS2
sbs2 <- signatures[["SBS2"]]

# Plot
sig_visualise(signature = sbs2, title = "SBS2")

```

We can do the same with doublets, indels or de novo signatures

```{r}
# Load Signature
signatures <- sig_load("COSMIC_v3.3_DBS_GRCh38")

# Select just SBS2
dbs9 <- signatures[["DBS9"]]

# Plot
sig_visualise(signature = dbs9, title = "DBS9")
```

### Custom Data and Palettes

`sig_visualise` allows users to provide custom colour mappings and therefore supports all manner of custom visualisations.

```{r}
# Create Custom Signature
sig_custom <- data.frame(
  type = c("INDELS", "INDELS", "SUBSTITUTIONS","SUBSTITUTIONS"),
  channel = c("INDELS", "DELETIONS", "SBS", "DOUBLETS"),
  fraction = c(0.1, 0.1, 0.7, 0.1)
  )

# Custom palette
 custom_pal <- c('INDELS' = "darkorange", "SUBSTITUTIONS" = "darkgreen")

# Plot
sig_visualise(signature = sig_custom, title = "Custom Signature", palette = custom_pal)
```
